Homicide Increases in the COVID-19 Era

### 2025-03-05 Draft3.qmd
Adding Draft 3 WIP

@@

@@

## Regression Between Median Income and Crimes per Zip Code

@@

# Spatio-Temporal Analysis of Crime in Los Angeles

```{r}
crimes_with_zips <- read.csv("0_Data/Cleaned_Data/crimes_with_zips.csv")

>>>>

crime_la$month <- lubridate::month(crime_la$DateParsed)

@@

# Plot bar chart with horizontal labels
barplot(crime_counts, col = "lightblue",
        xlab = "Day of the Week", ylab = "Number of Crimes",
        names.arg = names(crime_counts), las = 1, cex.names = 0.4, cex.axis = 0.6)
```

@@

## Regression Between Median Income and Crimes per Zip Code - DROP THIS

@@

## Chi-Square for Zip Code

```{r}
homicides_by_zip <- homicides %>% group_by(ZCTA5CE20) %>% summarize(HomicideCount = n()) %>% ungroup()
chisq.test(x = as.character(homicides_by_zip$ZCTA5CE20), y = homicides_by_zip$HomicideCount)
```

## Model Progression
### Initial Spatial Analysis of Crime in Los Angeles

```{r, echo=FALSE, warning=FALSE}
homicides_latlon_rounded <- homicides %>% mutate(LAT_rounded = round(LAT, 1),
                                                 LON_rounded = round(LON, 1))
homicides_lat_long <- homicides_latlon_rounded %>% group_by(LAT_rounded, LON_rounded) %>% summarize(HomicideCount = n()) %>% ungroup()

linear_model1 <- lm(HomicideCount ~ LAT_rounded + LON_rounded, data = homicides_by_year_lat_long)

summary(linear_model1) # longitude rounded is significant, LAT_rounded is not
```

### By Year
```{r}
homicides_lat_long <- homicides_latlon_rounded %>% group_by(LAT_rounded, LON_rounded) %>% summarize(HomicideCount = n()) %>% ungroup()

linear_model2 <- lm(HomicideCount ~ LAT_rounded + LON_rounded + year, data = homicides_by_year_lat_long)

summary(linear_model2) # longitude rounded is significant, LAT_rounded is not. Neither is year
```
